---
title: "R Character Manipulation and Date Processing"
author: "Lidiia Tronina"
date: "9/17/2017"
output: html_document
---
```{r}
library(stringr)
```

###Problem 3
Copy the introductory example. The vector name stores the extracted name.

```{r}
rawdata <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert" 
```

```{r}
name <- unlist(str_extract_all(rawdata, "[[:alpha:]., ]{2,}"))
name
```
a. Use the tools of this chapter to rearrange the vector so that all elements conform to the standard first_name last_name.

```{r}
name2 <- str_replace_all(name, pattern = "Dr.", replacement = ",")
name3 <- str_replace_all(name2, pattern = "Rev.", replacement = ",")
name3

```


b. Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.).

```{r}
title <- str_detect(name,"Rev.|Dr.")
titlelist <- data.frame (name, title)
titlelist
```
c. Construct a logical vector indicating whether a character has a second name

```{r}
mid_name <- str_detect(name," [A-Z]\\.")
midname_list<- data.frame (name, mid_name)
midname_list
```

###Problem 4

Describe the types of strings that conform to the following regular expressions and construct an example that is matched be the regular expression. 

a. Any digits before $ sign 


```{r}
sample <- "813921809328$zx"  
str_extract(sample, "[0-9]+\\$")
```
b.  It will extract word with 4 lower case letters.

```{r}
sample <- "dataproject lidia Test cuny"  
str_extract(sample, "\\b[a-z]{1,4}\\b")
```

c.

It will extract any charecters before ".txt", including ".txt"

```{r}
sample <- "queens.txt"  
str_extract(sample, ".*?\\.txt$")
```

d.

It will extract 2 digits prior "/" and than exctly 2 digits after and than "/" again following by 4 digits.

```{r}
sample <- "010/06/19920"  
str_extract(sample, "\\d{2}/\\d{2}/\\d{4}")
```

e.
It will extract charecter within  "< >" and between both tags. 

```{r}
sample = "<text1> text text text </text1>"
str_extract(sample, "<(.+?)>.+?</\\1>") 
```


###Problem 9


```{r}
code <- c("clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr")

```


```{r}
str_extract_all(code,"[A-Z]")
```
CONGRATULATIONS YOU ARE A SUPERNERD NERD :)
